Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-23 awipev-CO2.Rmd
sal_mix and temp_mix modifications done3

d_all$diff_sal_fb_insitu <- d_all$sal_insitu - d_all$sal_fb
mean_diff_sal_fb_insitu <- round(mean(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_sal_fb_insitu <- round(sd(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)

@@

```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}

@@

mean_TseaF_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all%>%
  dplyr::mutate(temp_insitu = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_insitu))

@@

mean_TseaF_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all%>%
  dplyr::mutate(temp_insitu = ifelse(datetime == "2019-09-13 13:00:00" , mean_TseaF_4h, temp_insitu))

#interpolation of salinity during the FB off maintenance
salinterp <-approx(d_all$datetime, d_all$sal_mix, xout=d_all$datetime, method="linear", rule=2)
names(salinterp) <- c("datetime", "sal_interp")
salinterp <- as.data.frame(salinterp)
d_all$sal_mix_interp <- salinterp$sal_mix_interp

d_all$sal_mix_interp <- ifelse(d_all$datetime > "2018-03-09 00:00:00" & d_all$datetime < "2018-04-16 16:00:00", d_all$sal_mix_interp, d_all$sal_mix)

@@

### **Calculated / Durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal_mix,temp, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp), !is.na(sal_mix))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal_mix, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

>>>>

d_all$diff_sal_fb_insitu <- d_all$sal_insitu_ctd - d_all$sal_fb
mean_diff_sal_fb_insitu <- round(mean(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_sal_fb_insitu <- round(sd(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)

@@

```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}

@@

mean_TseaF_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all%>%
  dplyr::mutate(temp_mix = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_mix))

@@

mean_TseaF_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all%>%
  dplyr::mutate(temp_mix = ifelse(datetime == "2019-09-13 13:00:00" , mean_TseaF_4h, temp_mix))

#interpolation of salinity during the FB off maintenance
salinterp <-approx(d_all$datetime, d_all$sal_mix, xout=d_all$datetime, method="linear", rule=2)
names(salinterp) <- c("datetime", "sal_mix_interp")
salinterp <- as.data.frame(salinterp)
d_all$sal_mix_interp <- salinterp$sal_mix_interp

d_all <- d_all %>%
  dplyr::mutate(sal_mix_interp =  ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-16 16:00:00", sal_mix_interp, sal_mix))

@@

### **Calculated / Durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal,temp, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp), !is.na(sal))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
